Monad Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis

### 2014-11-13 writeup/pldi15.tex
reworked semantics. continuations are now allocated. description of effects is done abstractly and concrete instances are given later.
unicode fixes.  abstract interpreter briefly described. most of the content is in. now to make it pretty :)
on the way to automating markdown -> latex
such automation. much amaze.
Typesetting.
last leg of typesetting
No copyright space.
fixed font, prose in progress
Cut typesetting.
fleshed out recovering interpreters section a little more
adding latex commands in markdown is now supported.
progress
...
added support for raw characters and rearranged macro expa

% any author declaration will be ignored  when using 'plid' option (for double blind review)
\documentclass[pldi]{sigplanconf}

@@

% \usepackage{SIunits}            % typset units correctly
\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

\usepackage{fontspec}
\setmonofont[Scale=0.7]{DejaVu Sans Mono}

@@

@@

\title{Modular Metatheory for Abstract Interpreters}
\maketitle

Abstract {-{
\begin{abstract}

@@

\end{abstract}
}-}

@@

>>>>

%lambdlambdaa any author declaration will be ignored  when using 'plid' option (for double blind review)
\documentclass[pldi,nocopyrightspace]{sigplanconf}

@@

% \usepackage{SIunits}            % typset units correctly
\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage{amsmath}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\floatstyle{boxed}
\restylefloat{figure}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}

% This makes newlines not introduce paragraphs.
% Paragraphs must be explicitly marked with \par
% WHAT WIZARDRY IS THIS
\endlinechar=9\relax

@@

\newcommand\litM{M}
\newcommand\litTime{Time}
\newcommand\litStore{Store}
\newcommand\litVal{Val}

\newcommand{\itop}[1]{\operatorname{\mathit{#1}}}
\newcommand{\ttbfop}[1]{\operatorname{\mathtt{\boldsymbol{\mathbf{#1}}}}}
\newcommand{\ttbfbin}[1]{\mathbin{\mathtt{\mathbf{\boldsymbol{#1}}}}}
\newcommand{\ttop}[1]{\operatorname{\mathtt{#1}}}
\newcommand{\Concrete}[1]{\mathtt{\mathbf{#1}}}
\newcommand{\Abstract}[1]{\widehat{\mathtt{\mathbf{#1}}}}

@@

% These are supposed to make align* not have breaks around it...
\setlength{\abovedisplayskip}{0em}
\setlength{\belowdisplayskip}{0em}
\setlength{\abovedisplayshortskip}{0em}
\setlength{\belowdisplayshortskip}{0em}

%\title{The Marriage of Monad Transformers and Abstract Interpreters: Modular Metatheory for Program Analysis}
\title{Monad Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis}
\authorinfo{David Darais}{Harvard University, USA}{darais@seas.harvard.edu}
\authorinfo{Matthew Might}{University of Utah, USA}{might@cs.utah.edu}
\authorinfo{David Van Horn}{University of Maryland, USA}{dvanhorn@cs.umd.edu}
\maketitle

% Abstract {-{
\begin{abstract}

@@

\end{abstract}
% }-}

@@

\bibliographystyle{abbrvnat}
\bibliography{dvanhorn,davdar}
